Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-10 R0V0.tex
Item 25
change email for contact

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt humberto.shiromoto@ieee.org}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
}

@@

\mypara Once $Q$ has been computed, employing Finsler's lemma \cite[Lemma~11.1]{CalafioreGhaoui2014} pointwisely, the existence of a function $Y:\mathbb{R}^n\to\mathbb{R}^{n\times m}$ satisfying MI~\eqref{eq:MI formulation} is ensured.

>>>>

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt h.stein.shiromoto@gmail.com}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
}

@@
